---
title: "README"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# GtR
This package provides a set of functions to search for UK research council funded projects from [Gateway to Research.](https://gtr.ukri.org/)

## Project Search 
You can search for projects associated with a search term- in the following example I will search for prjects associated with `social network analysis`

```{r sna_search,eval=TRUE,echo=TRUE,message=FALSE,warning=FALSE}
library(GtR)
library(kableExtra)

SNA_projects<-gtr_project_search("social network analysis")


kable(SNA_projects[1:3,])

```

## Extracting Project infromation 
The following functions extract information for projects. 

### Organisations
The first function extract information on the projects, and lists all of the organisational collaborators, including both academic and non academic organisations. 

This is done for an example project: ``
```{r org_ex,eval=TRUE,echo=TRUE,message=FALSE,warning=FALSE}
library(GtR)
library(kableExtra)
##Example URL
url<-"https://gtr.ukri.org/projects?ref=G0501806"


```


### Individuals
```{r ind_ex,eval=TRUE,echo=TRUE,message=FALSE,warning=FALSE}
library(GtR)
library(kableExtra)
##Example URL
url<-"https://gtr.ukri.org/projects?ref=G0501806"


```


## Impact & Publications
```{r imp,eval=TRUE,echo=TRUE,message=FALSE,warning=FALSE}
library(GtR)
library(kableExtra)
##Example URL
url<-"https://gtr.ukri.org/projects?ref=G0501806"


```
